\section{Scheduling Policies}\label{sec:policy}

In this section, we introduce the four policies in our system ---
{\em priority-based}, {\em proportion-based}, {\em workload-based}
and {\em deadline-based}.
Each policy requires different parameters such as job priority,
execution efficiency per different server and execution deadline.
{\em Decision maker} makes dispatching plans to according to a specified
policy.

%%% When designing the schedule policies, one should take the number of
%%% tasks a job is split into consideration since we don't want to assign
%%% workers more than tasks of a job to it.
%%% Recall that it is the end users' responsibility to split a job into well
%%% balanced tasks; the more balanced the tasks, the better the system
%%% schedules.


\subsection{Priority-based Policy}	%%% [DS] revise the first paragraph

%%% Introduce Priority-based
{\em Priority-based} distributes workloads according to job priority. 
We first sort all jobs in the system according to their priority in 
descending order.
Starts from the job with the highest priority, we assign $x$ workers to
the job, where $x = max(number of idle worker, number of tasks in the 
job)$.
The job is removed from the list.
The process is repeated until there are no idle workers or unassigned 
jobs.
The idea behind this policy is to make the job with highest priority 
runs as fast as possible.
However, this assignment might cause {\em starvation} to jobs with 
low priority

%%% How we avoid starvation from happening
To avoid {\em starvation}, we preserve a portion for low priority jobs.
We set a reservation rate $r \in [0,1]$ that the portion $r$ of workers
will be reserved for low priority jobs.
The job with highest priorities can use at most the $1-r$ of all workers
and the remaining workers, including those are not reserved but still not
assigned to the highest priority job because of the task amount limit,
will be assigned to jobs with lower priority, in the manner that one job
receives one worker.
The complete algorithm is shown as algorithm~\ref{algo:priority-based}.

\begin{algorithm}[htbp]
  \input{snippets/policies/priority-based-policy}
  \caption{Priority-based policy}
  \label{algo:priority-based}
\end{algorithm}

\subsection{Proportion-based Policy}	 %%% [DS] revised

The main concern of {\em Proportion-based} policy is the workload 
proportion of a job to all the others.
In contrast to {\em priority-based}, this policy does not take job 
priorities into consideration unless the priority of a task is strongly 
related to its workload.
The {\em Decision maker} first summing all the workloads from each job, 
then compute the ratio of the individual job.
The number of workers a job is assigned equals to the number of all 
workers multiplies it ratio.
This algorithm, as shown in algorithm~\ref{algo:proportion-based}, is
also known as {\em fair share scheduling}~\cite{cite:fair-share-scheduling}.
Workers a job should be allocated is in proportion to its workload 
proportion to all jobs. 

{\em Proportion-based} is a suitable solution for streaming jobs or jobs
with dependencies.  For streaming jobs with vary input rate, the number 
of workers needed is highly related to its input rate, thus workload.
As for jobs with dependencies, a job may need the output from other 
jobs as input.
Therefore, we should assign more workers to the predecessor in the 
beginning, and reduce the number of workers according to time.
On the other hand, the number of worker of a successor will be 
increasing since the workload from the predecessor increased.

% TODO For streaming jobs, workloads may varies: For streaming jobs
% dependent on others, if they don't have anything to process, its
% workload is low so no workers needed, but as results come out, we
% should give it servers.

\begin{algorithm}[htbp]
  \input{snippets/policies/proportion-based-policy}
  \caption{Proportion-based policy}
  \label{algo:proportion-based}
\end{algorithm}


\subsection{Workload-based Policy}       %%% [DS] revised

%%% [DS] The only different is worker heterogeneity?
%%% What is "workload requirement of $J_m$"

Similar to the {\em proportion-based} policy, the {\em workload-based}
policy takes the workload of jobs as scheduling metric.
However, {\em workload-based} takes worker heterogeneity, i.e. each
worker may have different computing ability, into consideration.
This policy tries to finish every job by assigning jobs to the most 
suitable workers, i.e. workers with higher throughput.

\subsubsection{Model Definition}

We represent each job $j_i$ submitted as $j_i = (w_i, p_i, n_i)$, where
$w_i$ is the estimated workload, $p_i$ is the job priority, and $n_i$
is the number of tasks in $j_i$.
As for the workers, we model each worker $s_k$ as a vector of estimated
{\em throughput} of each submitted job; we can write is as $s_k =
(th^k_1, th^k_2, \ldots)$.

\subsubsection{Algorithm}

We apply greedy approach in this policy.
First, we sort all the jobs according to their priority in descending
order.
Starts from the job with the highest priority $J_m$, sort the remaining
workers according to their throughput $th_m$ to $J_m$.
Then assign the top $k$ workers that can satisfy the workload
requirement of $J_m$, and remove assigned workers from the list.
The job is also removed from the list waiting for assignment.
Repeat this process until there are no idle worker or un-assigned job.
The complete algorithm is shown as algorithm ~\ref{algo:workload-based}.

\begin{algorithm}[htbp]
\input{snippets/policies/workload-based-policy}
\caption{Workload-based policy}
\label{algo:workload-based}
\end{algorithm}


\subsection{Deadline-based Policy}	%%% [DS] revised

{\em Deadline-based} policy tries to finish every jobs before their 
deadline.
If a feasible scheduling plan does not exist, this policy tends to meet
the deadlines for jobs with higher priority.
There are varies kinds of jobs that must be finished before a given 
time constraint.
For example, as a Internet service provider, settling monthly bills of
millions of users within few days after the monthly charge-off day is
very critical to their business.
It it obvious that computing resource allocated to this kind of job 
should increase as their deadline approaches --- the closer the 
deadline is, the more worker a job should get.
Unfortunately, policies introduced above does not directly adapt to 
this need; hence, we introduce this policy designed for
{\em deadline-aware} scenarios.

\subsubsection{Model Definition}

For this policy, we assume that each job is provided with priority and
deadline.
The execution time for each job is assumed to be known, which can be 
estimated by historical data or profiling.
A job $j_i$ can thus be represented as $j_i = (d_i, p_i, n_i)$, where
$d_i, p_i, n_i$ refers to the job deadline, job priority, and the 
number of tasks in $j_i$, respectively
The workers are modeled as a vector of estimated execution time of each 
submitted job: $s_k = (T^k_1, T^k_2, \ldots)$, similar to the previous 
policy.

\subsubsection{Algorithm}

A job should be finished before its deadline.
Intuitively, for the same job, if the deadline is twice tighter, it
requires twice as many workers to meet that deadline.
More generally speaking, the deadline and the workload are in reciprocal
relationship.
This implies that an worker allocation $S$ to job $j_i$ meeting the
deadline is equivalent to
\[\displaystyle\sum_{s_k \in S}\frac{1}{T^k_{j_i}} \geq \frac{1}{d_i}\]
With this observation, only a little modification on the {\em workload-based}
policy is needed to apply to this model: simply use the inverse of
deadline as throughput.

First, we sort all the jobs according to their priority in descending
order.
Starts from the job with the highest priority $J_m$, sort the remaining
workers according to their throughput $th_m$ to $J_m$.
Then assign the top $k$ workers that can finish $J_m$ before it 
deadline, and remove assigned workers from the list.
The job is also removed from the list waiting for assignment.
Repeat this process until there are no idle worker or un-assigned job.
The complete algorithm is shown as algorithm ~\ref{algo:deadline-based}.

\begin{algorithm}[htbp]
  \input{snippets/policies/deadline-based-policy}
  \caption{Deadline-based policy}
  \label{algo:deadline-based}
\end{algorithm}

