\section{Introduction}

\begin{frame}
  \frametitle{Background}
  \setbeamercovered{transparent}
  \begin{itemize}[<+->]
    \item As the amount of data and computing demand increases, more and
      more companies tend to build their own data centers --- Private
      Cloud.
    \item For elasticity, rather than dedicating servers for particular
      applications, more people tend to build a large cluster for all
      needs.
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Background --- Job Characteristics}
  \setbeamercovered{transparent}
  In data centers, jobs come with different characteristics.
  \begin{itemize}[<+->]
    \item <+(1)->Importance/Priority
    \item <+(1)->Computation resource demand
      \begin{itemize}
        \item <+(1)-> CPU bound versus I/O bound
        \item <.(1)-> Requires large RAM
        \item <.(1)-> Leverage GPGPU
      \end{itemize}
    \item <.(3)->{\alert{Deadline/Service Level Agreement}}
  \end{itemize}
  \onslide<+(1)->{Moreover, some of them should be completed before time
    constraints.
    \begin{itemize}
      \item <.(1)-> Billing jobs should be done within days after
        charge-off.
      \item <.(1)-> Research experiments are not that urgent.
    \end{itemize}
  }
\end{frame}
\begin{frame}
  \frametitle{Background --- Server Characteristics}
  \setbeamercovered{transparent}
  \begin{itemize}[<+->]
    \item Resources in data centers are usually \emph{limited} and
      \emph{fixed}
      \begin{itemize}
        \item Purchase new ones and remove obsolete ones only on
          periodic equipment upgrades.
        \item \textbf{The number of workers is fixed between upgrades.}
      \end{itemize}
    \item <.(-2)-> Servers in the cluster are \alert{heterogeneous}.
      \begin{itemize}
        \item Old servers coexist with new servers.
        \item <.-> Only few servers have special capabilities, like Giga-LAN
          or GPGPU.
      \end{itemize}
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Goal}
  \begin{itemize}
    \item Implement a resource management component that \emph{dynamically}
      adjusts resource for each job.
    \item System administrator can easily specify different policies to
      adapt to their needs.
    \item The system should take server \alert{heterogeneity} into consideration.
  \end{itemize}
\end{frame}
\begin{frame}
  \frametitle{Target Environment --- CHT's Data Center}
  \begin{itemize}
    \item Physical servers only +
      JPPF\footnote[frame]{\tiny\fullcite{cite:JPPF}}.
    \item Old and new servers coexists --- heterogeneous environment.
    \item Most jobs process files (billing accounting).
    \item Jobs are split into many \emph{tasks}, each can be processed
      in parallel.
    \item Data is shared via NFS.
    \item Servers may fail.
  \end{itemize}
\end{frame}

